Speed estimation for vehicles using \\SVM classification and edge detection

### 2016-06-15 Administratie/report/paper.tex
update paper

\subsection{Zebra crossings}

\subsection{Combination of classification and edge detection}

The combination of road classification and edge detection starts with removing outliers from the road classification. The goal of this is to eliminate the effect an outlier would have when it's close to the car. A non-road block is considered an outlier when it has less than 4 non-road block neighbours. This is repeated until we become a stable condition without outliers.

Next, the edges are checked if they aren't on the road. This is done by checking that an edge is on a non-road block of the road classification. For safety reasons there is an additional check. The above, left and right blocks of an edge should also be considered as non-road.

When the edge is not classified on the road, it is added to a collection. The intersections of the edges in the collection and the masks are computed. For each frame the masks give the projected trajectory of the car. 
The edges are visualised as blue lines on figure \ref{zebra}. The intersections are shown green. The closest intersection to the car is shown in red. At this point the maximum speed is derived from the intensity.

@@

@@

\subsection{Driving results}
To combine road classification and edge detection we should first look at the performance of these two methods separately. Therefore, the evaluation was run on each of these two methods. The result is shown in figure \ref{distance_result}. The first bar of the histogram shows for every dataset the performance of road classification. Because of a crash in the first dataset there can only be travelled 317m. The second bar shows for each dataset the distance travelled only relying on edge detection. There are no crashes in the four datasets so the results are better.

A first and very safe way to combine these two methods is the following. A region is considered road only if it's identified as road by the road classification and there is no edge. The performance of this combination is shown in the third bar. As said this is very safe, therefore the travelled distance is lower than only applying edge detection.

An other way to make a combination, witch still results in zero crashes is to focus on edge detection. A region is considered road if there are no edges. When there are edges, road classification is used to decide whether it's road. This strategy gave us the best results and are shown as the fourth bar.
\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth]{fig/distance_result.png}
	\caption{Results of road classification, edge detection and combinations.\label{distance_result}}
\end{figure}

>>>>

\subsection{Zebra crossings}
TODO

\subsection{Combination of classification and edge detection}\label{method-combination}

For each frame the given masks show the projected trajectory of the car. Intersections get calculated in order to find the road where it's safe to drive. The edges of the edge detection are visualized as blue lines on figure \ref{visualization}. The intersections are shown in green. The closest intersection to the car is shown in red. At this point the maximum speed is derived from the intensity of this pixel.

In order to calculate the edges, both road classification and edge detection are combined. Therefor two strategies were tested:
\begin{enumerate}
\item  A region is considered to be road only if it's identified as road by the road classification and there are no edges. Both classification and edge detection should indicate a pixel as road in order to be used for safe driving.
\item A region is considered to be road if there are no edges. When edges are detected, road classification is used to decide what part of the image is road. 
\end{enumerate}

Both strategies start by removing outliers from the road classification. The goal of this is to eliminate the effect an outlier would have when it's close to the car. A non-road block is considered an outlier when it has less than 4 non-road block neighbours. This is repeated until all outliers are removed.

For the first strategy the edges of the classification are computed. These get combined with the edges from the edge detection. The closest intersection of any edge with the given mask of the image is used to calculate the maximum speed of the vehicle.

In the second strategy, the edges are checked if they aren't on the road. This is done by checking that an edge is on a non-road block of the road classification. For safety reasons there is an additional check. The above, left and right blocks of an edge should also be considered as non-road. When the edge is not classified as road, it is added to a collection. The intersections of the edges in the collection and the masks are then computed.

\begin{figure}[t]
  \centering
  \includegraphics[width=.9\textwidth]{fig/frame00025.png}
  \caption{Visualization of a processed frame showing both classification and edge detection}
  \label{visualization}
\end{figure}

@@

todo: geen schatten van edge detection meer

@@

\subsection{Driving results}
Driving results get evaluated using a script that calculates the distance a vehicle can drive in one minute, based on the given speed by our system. This script includes a ''ground truth'' for each frame in each dataset. If our speeds exceed this ground truth, the vehicle crashes and is not able to continue driving.

In section \ref{method-combination} two strategies were presented. These use a combination of classification and edge detection. First, the evaluation was run separately on these two methods. The results are shown in figure \ref{distance_result}. The first bar of the histogram shows for every dataset the performance of road classification. Because of a crash in the first dataset there can only be traveled 317m (out of the 1350m). The second bar shows for each dataset the distance traveled only relying on edge detection. There are no crashes in the four datasets so we can say these results are way better. This makes us believe the second combination strategy will be the better one, as it relies.

TODO: maximum met edge detection voor elke dataset? 1350,

The first way of combining the two methods is very safe and thus results in no crashes over the four datasets. A region is considered to be road only if it's identified as road by the road classification and if there are no edges. Both classification and edge detection should indicate a pixel as road in order to be used for safe driving. The performance of this combination is shown in the third bar of figure \ref{distance_result}. As said, this strategy is very safe, giving up a lot of traveled distance in favor of safety.

The second strategy for combination also results in zero crashes over the four datasets. This strategy tries to focus on edge detection. A region is considered road if there are no edges. When there are edges, road classification is used to decide whether it's road or not. This strategy gave us the best results, as shown in figure \ref{distance_result} as the fourth bar.
\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth]{fig/distance_result.png}
	\caption{Results of road classification, edge detection and combinations.\label{distance_result}}
\end{figure}
